Handling String-Number Conversion in String Constraint Solving

### 2019-11-12 evaluation.tex
a note about PyEx

We have implemented the proposed approach in a prototype tool \textsf{z3-Trau} as a part of the Z3 theorem prover. This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports. Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to parse input formulae.

@@

Occasionally, during the experiments, there was a case where a solver reported a different answer to a test than the other solvers. To decide which solver reported the incorrect answer, we have developed our own validator. Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test. The modified test is re-evaluated by solvers and if the solvers decide that the modified test is satisfiable, the answer of the solvers that originally reported unsat is evaluated as incorrect.

>>>>

We have implemented the proposed approach in a prototype tool \textsf{z3-Trau} as a part of the Z3 theorem prover. This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports. Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.

@@

Occasionally, during the experiments, there was a case where a solver reported a different answer to a test than the other solvers. To decide which solver reported the incorrect answer, we have developed our own validator. Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test. The modified test is re-evaluated by solvers. If the solvers decide that the modified test is satisfiable, the answer of the solvers that initially reported unsat is evaluated as incorrect.

\paragraph{A Comparison with other tools on well-known benchmarks.}
In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in many cases even better. This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that was created by others and that contain a very few formulae with constraints of string-number and number-string conversion.

The first benchmark is called PyEx according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing. This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests. PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints. Although this benchmark was created by cvc4 group and cvc4 solved more SAT cases than the other tools, z3-trau was behind by less than 1\textperthousand\ of cases and moreover managed to solve the most UNSAT cases.
